A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
zjenja: minor edits
describe dataset

\section{Validation}

@@

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
For each strategy, we measured the angle between consecutive segments.
The relative frequency of these angles is shown in \cref{smoothness}.
While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.

>>>>

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in \cref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices.

@@

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive segments generated by each strategy.
The relative frequency of these angles is shown in \cref{smoothness}.
All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.
